KidsAIR initial SUMs data work

### 2020-01-22 home_child_data_cleaning.Rmd
data cleaning updates

# create dataset of child demographic data
wmt_child_demographics <- joined1 %>% 
  distinct(child_id_num, .keep_all = TRUE) %>% 
  arrange(home_id, child_id_num, winter_id) %>% 
  filter(enrolled == 1)

# Save as RDS and CSV
write_rds(wmt_home_ids_linked, "Output/wmt_ids_linked.rds")
write_rds(wmt_child_demographics, "Output/wmt_demographic_data.rds")
write_csv(wmt_home_ids_linked, "Output/wmt_ids_linked.csv")
write_csv(wmt_child_demographics, "Output/wmt_demographic_data.csv")
```

@@

# create dataset of child demographic data
nn_child_demographics <- joined1 %>% 
  distinct(child_id_num, .keep_all = TRUE) %>% 
  arrange(home_id, child_id_num, winter_id) %>% 
  filter(enrolled == 1)

# Save as RDS and CSV
write_rds(nn_home_ids_linked, "Output/nn_ids_linked.rds")
write_rds(nn_child_demographics, "Output/nn_demographic_data.rds")
write_csv(nn_home_ids_linked, "Output/nn_ids_linked.csv")
write_csv(nn_child_demographics, "Output/nn_demographic_data.csv")
```

@@

# create dataset of child demographic data
ak_child_demographics <- joined1 %>% 
  distinct(child_id_num, .keep_all = TRUE) %>% 
  arrange(home_id, child_id_num, winter_id) %>% 
  filter(enrolled == 1)

# Save as RDS and CSV
write_rds(ak_home_ids_linked, "Output/ak_ids_linked.rds")
write_rds(ak_child_demographics, "Output/ak_demographic_data.rds")
write_csv(ak_home_ids_linked, "Output/ak_ids_linked.csv")
write_csv(ak_child_demographics, "Output/ak_demographic_data.csv")
```

>>>>

# create dataset of child demographic data
wmt_child_demographics <- joined1 %>% 
  #distinct(child_id_num, .keep_all = TRUE) %>% 
  arrange(home_id, child_id_num, winter_id) %>% 
  filter(winter_id == 1 | winter_id == 2)

# Save as RDS and CSV
write_rds(wmt_home_ids_linked, "Output/wmt_ids_linked.rds")
write_rds(wmt_child_demographics, "Output/wmt_demographic_data.rds")
```

@@

# create dataset of child demographic data
nn_child_demographics <- joined1 %>% 
  #distinct(child_id_num, .keep_all = TRUE) %>% 
  arrange(home_id, child_id_num, winter_id) %>% 
  filter(winter_id == 1 | winter_id == 2)

# Save as RDS and CSV
write_rds(nn_home_ids_linked, "Output/nn_ids_linked.rds")
write_rds(nn_child_demographics, "Output/nn_demographic_data.rds")
```

@@

# create dataset of child demographic data
ak_child_demographics <- joined1 %>% 
  #distinct(child_id_num, .keep_all = TRUE) %>% 
  arrange(home_id, child_id_num, winter_id) %>% 
  filter(winter_id == 1 | winter_id == 2)

# Save as RDS and CSV
write_rds(ak_home_ids_linked, "Output/ak_ids_linked.rds")
write_rds(ak_child_demographics, "Output/ak_demographic_data.rds")
```

### 2020-01-22 placebo_exposure_data_cleaning.Rmd
data cleaning updates

---
title: "KidsAIR: placebo home exposure paper data cleaning"
author: "Ethan Walker"
date: "Started 21 Jan 2020, Updated 21 Jan 2020"
output: pdf_document
---

@@

# Filter winter 1 and placebo homes from PM dataset
## These homes will be the focus of the initial exposure abstract/paper
```{r}
pm_homes <- pm_clean %>% 
  filter(winter_id == 1) %>% 
  filter(treatment == "Placebo") %>% 
  group_by(area, home) %>% 
  mutate(initial_obs = if_else(pm_datetime_new == first_datetime_new, 1, 0)) %>% 
  filter(initial_obs == 1) %>% 
  mutate(pm_home = "true") %>% 
  select(area, home, home_winter_id, pm_home) %>% 
  ungroup() %>% 
  arrange(area, home)
```

# Join selected homes from above with other datasets and filter homes of interest

# PM data
## 93 placebo homes from Winter 1 have PM data
```{r}
pm_filtered <- pm_clean %>% 
  left_join(pm_homes, by = c("area", "home")) %>% 
  filter(select_home == "select") %>% 
  filter(winter_id == 1) %>% 
  #group_by(area, home) %>% 
  #summarize(n())
  ungroup() %>% 
  arrange(area, home)
```

# SUMs data
## 78 placebo homes from Winter 1 have SUMs data
#### Look for missing files/data? ####
```{r}
sums_filtered <- sums_clean %>% 
  left_join(pm_homes, by = c("area", "home")) %>% 
  filter(select_home == "select") %>% 
  filter(winter_id == 1) %>% 
  #group_by(area, home) %>% 
  #summarize(n())
  ungroup() %>% 
  arrange(area, home)

sums_homes <- sums_clean %>% 
  mutate(sums_home = "true") %>% 
  left_join(pm_homes, by = c("area", "home", "home_winter_id")) %>% 
  filter(pm_home == "true") %>% 
  filter(winter_id == 1) %>% 
  distinct(home, .keep_all = TRUE) %>% 
  mutate(sums_pm_match = "true") %>% 
  select(home, area, home_winter_id, winter_id, home_id, treatment, 
         sums_home, sums_pm_match)

sums_pm_check <- pm_homes %>% 
  left_join(sums_homes, by = c("area", "home", "home_winter_id")) %>% 
  filter(is.na(sums_pm_match))

# Should have SUMs data for YKC06113
# Should have SUMs data for CH107, CH218
# No files for CH102, CH103 (file but no content), CH106, TC357 
# Should have SUMs data for WMA102, WMA132, WMA141
# No files for WMA507, WMA673
# Download files for WMA114, WMA121, WMA125

check <- sums_clean %>% 
  filter(home == "YKC06113")
```

# Demographics data
## 91 placebo homes from Winter 1 have demographic data
#### Look for missing files/data? ####
```{r}
demographics_filtered <- demographics_clean %>% 
  left_join(pm_homes, by = c("area", "home")) %>% 
  filter(select_home == "select") %>% 
  filter(winter_id == 1) %>% 
  #group_by(area, home) %>% 
  #summarize(n())
  ungroup() %>% 
  arrange(area, home)
```

>>>>

---
title: "KidsAIR: placebo home exposure paper data cleaning"
author: "Ethan Walker"
date: "Started 21 Jan 2020, Updated 22 Jan 2020"
output: pdf_document
---

@@

# Filter winter 1 and placebo homes from PM dataset
## These homes will be the focus of the initial exposure abstract/paper
```{r}
# 93 Winter 1 placebo homes have PM data
pm_homes_placebo <- pm_clean %>% 
  filter(winter_id == 1) %>% 
  filter(treatment == "Placebo") %>% 
  group_by(area, home) %>% 
  mutate(initial_obs = if_else(pm_datetime_new == first_datetime_new, 1, 0)) %>% 
  filter(initial_obs == 1) %>% 
  mutate(pm_home = "true") %>% 
  select(area, home, home_winter_id, pm_home) %>% 
  ungroup() %>% 
  arrange(area, home)

# 88 Winter 1 education homes have PM data
pm_homes_education <- pm_clean %>% 
  filter(winter_id == 1) %>% 
  filter(treatment == "Education") %>% 
  group_by(area, home) %>% 
  mutate(initial_obs = if_else(pm_datetime_new == first_datetime_new, 1, 0)) %>% 
  filter(initial_obs == 1) %>% 
  mutate(pm_home = "true") %>% 
  select(area, home, home_winter_id, pm_home) %>% 
  ungroup() %>% 
  arrange(area, home)

# 86 Winter 1 filter homes have PM data
pm_homes_filter <- pm_clean %>% 
  filter(winter_id == 1) %>% 
  filter(treatment == "Filter") %>% 
  group_by(area, home) %>% 
  mutate(initial_obs = if_else(pm_datetime_new == first_datetime_new, 1, 0)) %>% 
  filter(initial_obs == 1) %>% 
  mutate(pm_home = "true") %>% 
  select(area, home, home_winter_id, pm_home) %>% 
  ungroup() %>% 
  arrange(area, home)
```

#### Join selected homes from above with other datasets and filter homes of interest ####

# PM data
## 93 placebo homes from Winter 1 have PM data
## 88 education homes from Winter 1 have PM data
## 86 filter homes from Winter 1 have PM data
## All data is accounted for; missing data is truly missing from data collection issues
```{r}
pm_filtered <- pm_clean %>% 
  left_join(pm_homes_placebo, by = c("area", "home")) %>% 
  filter(pm_home == "true") %>% 
  filter(winter_id == 1) %>% 
  filter(treatment == "Placebo") %>% 
  ungroup() %>% 
  arrange(area, home)

pm_obs <- pm_clean %>% 
  left_join(pm_homes_placebo, by = c("area", "home")) %>% 
  filter(pm_home == "true") %>% 
  filter(winter_id == 1) %>% 
  group_by(area, home) %>% 
  summarize(n())
```

# SUMs data
## 80/93 placebo homes from Winter 1 have SUMs data
## 77/88 education homes from Winter 1 have SUMs data
## 70/86 filter homes from Winter 1 have SUMs data
## All data is accounted for; missing data is truly missing from data collection issues
```{r}
sums_filtered <- sums_clean %>% 
  # change to correct joining data of interest
  left_join(pm_homes_filter, by = c("area", "home")) %>% 
  filter(pm_home == "true") %>% 
  filter(winter_id == 1) %>% 
  #group_by(area, home) %>% 
  #summarize(n())
  ungroup() %>% 
  arrange(area, home)
```

# Demographics data
## 93/93 placebo homes from Winter 1 have demographic data
## 88/88 education homes from Winter 1 have demographic data
## 86/86 filter homes from Winter 1 have demographic data
```{r}
demographics_check1 <- demographics_clean %>% 
  # change to correct joining data of interest
  left_join(pm_homes_filter, by = c("area", "home")) %>% 
  filter(pm_home == "true") %>% 
  filter(winter_id == 1) %>% 
  group_by(area, home) %>% 
  summarize(n())

demographics_check2 <- demographics_clean %>% 
  # change to correct joining data of interest
  left_join(pm_homes_filter, by = c("area", "home")) %>% 
  filter(pm_home == "true") %>% 
  filter(winter_id == 1) %>% 
  group_by(area, home) %>% 
  summarize(n()) %>% 
  mutate(dem_filtered = "true") %>% 
  # change to correct joining data of interest
  full_join(pm_homes_filter, by = c("area", "home"))

demographics_filtered <- demographics_clean %>% 
  # change to correct joining data of interest
  left_join(pm_homes_filter, by = c("area", "home")) %>% 
  filter(pm_home == "true") %>% 
  filter(winter_id == 1) %>% 
  ungroup() %>% 
  arrange(area, home)
```

### 2020-01-22 sums_data_cleaning.Rmd
data cleaning updates

check_dates <- ak_sums_filtered %>% 
  group_by(home) %>% 
  distinct(datetime_sums, .keep_all = TRUE)
```

@@

>>>>

check_dates <- wmt_sums_filtered %>% 
  group_by(home) %>% 
  distinct(datetime_sums, .keep_all = TRUE)
```

@@

# Check to see if there are missing files to search for
## Through 22 Jan 2020, all files are accounted for that are not documented as missing
## Update once data collection is finished in April 2020
```{r}
# Load SUMs data
sums_clean <- read_rds("Output/sums_clean.rds")

check <- sums_clean %>% 
  filter(home_winter_id == 82 & area == "AK")

# Load SUMs data logs
wmt_sums_log <- read_rds("Output/wmt_sums_data_log.rds") %>% 
  mutate(area = "WMT")
nn_sums_log <- read_rds("Output/nn_sums_data_log.rds") %>% 
  mutate(area = "NN")
ak_sums_log <- read_rds("Output/ak_sums_data_log.rds") %>% 
  mutate(area = "AK")

# Combine SUMs logs from all areas
all_sums_log <- rbind(wmt_sums_log, nn_sums_log, ak_sums_log) %>% 
  mutate(winter_id = as.character(winter_id),
         sums_log = "true")

sums_check <- sums_clean %>% 
  group_by(area, home, winter_id) %>% 
  distinct(home, .keep_all = TRUE) %>% 
  full_join(all_sums_log, by = c("area", "home", "winter_id")) %>% 
  ungroup() %>% 
  arrange(area, home, winter_id)

#write_csv(sums_check, "Output/sums_check.csv")
```
